\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System

### 2024-08-14 Paper/Paper.tex

	\vspace{0.5cm}
	\tableofcontents

	\pagebreak

@@

	\section{Model Overview}

@@

		\begin{itemize}
			\item Branch retinal vein occlusion (BRVO) or hemicentral retinal vein occlusion (HCRVO)

			\item Central retinal vein occlusion (CRVO)

			\item Central serous chorioretinopathy (CSC)

			\item Dry age-related macular dystrophy (dry AMD)

			\item Epiretinal membrane (ERM)

			\item Macular hole (MH)

			\item Macular telangiectasia (Mactel)

			\item Mild diabetic retinopathy (mild DR)

			\item Referable diabetic retinopathy (referable DR)

			\item Retinitis pigmentosa (RP)

			\item Stargardt disease (Stargardt)

			\item Wet age-related macular dystrophy (wet AMD)
		\end{itemize}

		No real data. use the following criteria

@@

		Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model. OCT-Model and Fundus-Model are collectively called the Abnormity-Models. They use the same architecture (ResNet152, flatten to 2048 features, and fc). Diagnosis Model consists of #num submodels, one of which is for normal, and the other ones for each disease. each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.

@@

@@

		how to find grade (number of traits = grade for the disease as label during training), output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1]. )

@@

			Table: Data source for OCT
				numbered list of sources
				columns for source number, final column = total number of imgs
				rows for abnormities

			CycleGAN
				Fig: Intro
				Table: selection rates
				selection criteria

			transforms for OCT
				for train: copy, flip, randomcomb1
				for test: copy, flip, randomcomb2 -> explain truthfulness

			Table: Data source for Fundus - same as OCT

			Why I did not GAN Fundus

			transforms for Fundus
				similar to OCT
				explain differences

@@

			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...

@@

@@

@@

			how to choose data (with an example)

@@

			parameters used

@@

@@

			Fig: accuracy and loss over epochs
				trainAcc, validAcc, trainLosses, validLosses
			Table: for each disease:
				accuracy (only present accuracy for TOTAL)
				precision
				recall/sensitivity
				specificity
				F1
				AUC
			Fig: ROC for each disease

@@

		Strengths and weaknesses

>>>>

	\section*{Abstract}

	\pagebreak
	\vspace{0.5cm}
	\tableofcontents
	\pagebreak

@@

	\section{Overview}

@@

		No real data. use the following criteria. source for criteria

@@

@@

		Model consists of 3 parts: OCT-Model, Fundus-Model, and Diagnosis-Model. OCT-Model and Fundus-Model are collectively called the Abnormity-Models. They use the same architecture (ResNet152, flatten to 2048 features, and fc). Diagnosis Model consists of num submodels, one of which is for normal, and the other ones for each disease. each submodel first fuses output from both Abnormity-Models, then uses an fc to get final results for normal or for the disease.

@@

		output

@@

			Fig: overall flowchart

			Table: Data source for OCT and Fundus
				numbered list of sources
				columns for source number, final column = total number of imgs
				rows for abnormities

			CycleGAN
				Fig: Intro
				Table: selection rates
				selection criteria
				Why I did not GAN Fundus

			transforms for OCT
				for train: copy, flip, randomcomb1
				for test: copy, flip, randomcomb2 -> explain truthfulness
				explain differences between train and test, OCT and fundus

			Table: all data source

@@

			crossentropyloss, ADAM optimizer with LR 1e-3, batchSize 16, number of epochs...
			running time

@@

			time per image

@@

				comparison to other studies

@@

			how to choose data (with an example)
			how to find grade (number of traits = grade for the disease as label during training)

@@

			parameters used
			running time
			Fig: accuracy and loss over epochs
				trainAcc, validAcc, trainLosses, validLosses

@@

			output - calculate expected grade. in order to compare, divide by total number of traits for this disease so that normalized grade falls in [0, 1].

			Table: for each disease:
				accuracy (only present accuracy for TOTAL)
				precision
				recall/sensitivity
				specificity
				F1
				AUC
			Fig: confusion matrix (is it suitable?)
			Fig: ROC for each disease

	\section{Discussion}

@@

		Strengths and weaknesses
		how to improve

@@
